---
title: "Statistical Inference Course Project"
author: "Maciej Gielnik"
date: "15/11/2020"
output:
  pdf_document: default
  html_document: default
---
# Overwiew
In this project for Statistical Inference course I will report my results of exponential distribution simulation and basic inferential data analysis of the tooth growth in Guinea Pigs supplemented with a vitamin C.

#  Part 2: Basic Inferential Data Analysis Instructions

Loading ggplot2 and datasets. Changing dose and supp as a factor.

```{r load}
library(datasets)
library(ggplot2)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
ToothGrowth$supp <- as.factor(ToothGrowth$supp)
```

## Creating exploratory plot.
``` {r exploratory plots, fig.height = 1.5, fig.width = 4}
a <- ggplot(ToothGrowth, aes(x = dose, y = len, fill = supp))
a <- a + geom_boxplot()
a
```

## Splitting data into numeric vectors - see supplement
``` {r splitting,  echo=FALSE}
lenVC05 <- ToothGrowth [1:10, 1]
lenVC10 <- ToothGrowth [11:20, 1]
lenVC20 <- ToothGrowth [21:30, 1]
lenOJ05 <- ToothGrowth [31:40, 1]
lenOJ10 <- ToothGrowth [41:50, 1]
lenOJ20 <- ToothGrowth [51:60, 1]
```

## Calculating summary of tooth length for each dose of vitamin C and each supplement type.
```{r summary}
summary(lenVC05)
summary(lenVC10)
summary(lenVC20)
summary(lenOJ05)
summary(lenOJ10)
summary(lenOJ20)
```

## Testing if the dose of vitamin C from supplementation with ascorbic acid correspond to tooth length.
I have used independent 2-group t-test with unequal variances.
``` {r VC}
t.test(lenVC05, lenVC10, paired = FALSE, var.equal = FALSE)
t.test(lenVC05, lenVC20, paired = FALSE, var.equal = FALSE)
```
**The bigger the dose, the longer the teeth (p-value = 6.811e-07 and p-value = 4.682e-08 respectively). The same is true for the supplementation with Orange Juice, see supplement**

## Testing if there are differences between supplement type and tooth length.
I have used independent 2-group t-test with unequal variances.
``` {r diff}
t.test(lenVC05, lenOJ05, paired = FALSE, var.equal = FALSE)
t.test(lenVC10, lenOJ10, paired = FALSE, var.equal = FALSE)
t.test(lenVC20, lenOJ20, paired = FALSE, var.equal = FALSE)
```
**For doses 0.5 and 1.0 tooth length is bigger for the orange juice than for ascorbic acid (p = 0.006359 and p = 0.001038 respectively).**
**For dose 2.0 there is no difference between supplement types and tooth length (p = 0.9639).**


# Supplement

## Splitting data into numeric vectors 
``` {r splitting2}
lenVC05 <- ToothGrowth [1:10, 1]
lenVC10 <- ToothGrowth [11:20, 1]
lenVC20 <- ToothGrowth [21:30, 1]
lenOJ05 <- ToothGrowth [31:40, 1]
lenOJ10 <- ToothGrowth [41:50, 1]
lenOJ20 <- ToothGrowth [51:60, 1]
```

## Testing if the dose of vitamin C from supplementation with orange juice correspond to tooth length.
I have used independent 2-group t-test with unequal variances.
``` {r OJ}
t.test(lenOJ05, lenOJ10, paired = FALSE, var.equal = FALSE)
t.test(lenOJ05, lenOJ20, paired = FALSE, var.equal = FALSE)
```
**The bigger the dose, the longer the teeth**


