---
title: "Statistical Inference Course Project"
author: "Maciej Gielnik"
date: "15/11/2020"
output:
  pdf_document: default
  html_document: default
---
## Overwiew
In this project for Statistical Inference course I will report my results of exponential distribution simulation and basic inferential data analysis of the tooth growth in Guinea Pigs supplemented with a vitamin C.

## Part 1: Simulation Exercise Instructions
I simulate the exponential distribution with 40 observations and lambda = 0.2. Then I calculate the mean of the distribution and the variance of the distribution. I store means in means variable and variance in variance variable. I repeat that process 1000 times.

```{r sim}
means <- NULL
variance <- NULL
for (i in 1:1000) {
    means <- c(means,  mean (rexp(40, rate = 0.2)))
    variance <- c (variance, var(rexp(40, rate = 0.2)))
} 
```

For the exponential distribution

$$
mean = 1/lambda
$$
Therefore with lambda = 0.2 mean od this distribution should be equal to 5.

I make a histogram of means and calculate the mean

```{r mean, fig.height = 3, fig.width = 4}
hist(means, xlab = "mean", main = "mean of the exponantial distribution", breaks = 20)
mean(means)
```
Calculated mean is very close to 5.

Also for the exponential distribution

$$
{standard}_{deviation} = 1/lambda
$$
And
$$
variance = ({standard}_{deviation})^2
$$
Therefore:
$$
variance = (1/lambda)^2
$$

With lambda = 0.2 variance have to be equal to 25.

I make a histogram of variance and calculate the variance

```{r variance, fig.height = 3, fig.width = 4}
hist(variance, xlab = "variance", main = "variance of the exponantial distribution", breaks = 50)
mean(variance)
```
Calculated variance is close to 25.

The histogram distribution of means was changed to a density. A normal distribution with mean of 5 and sigma = sd (means) was drawn with a line. The distribution is approximately normal.

``` {r density}
hist(means, breaks = 50, freq = FALSE, xlim = c(1, 10))
x <- seq(min(means), max(means), length = 100)
y <- dnorm(x, 5, sd = sd(means))
lines(x, y)

```




